---
title: "Home"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---
```{r setup, include=FALSE}
library(knitr)
```

```{r cars, out.width="20%", fig.align='right', echo=FALSE}
img1_path <- "Pictures/Profile_head_small.png"
include_graphics(img1_path)
```

## Hello!

I'm Christophe, a PhD student at Durham University. For my PhD I work on [Rubyspot damselflies](https://www.inaturalist.org/projects/smoky-rubyspots) (Hetaerina) and how behavioural interference between species could impact their ability to range shift. I use a combination of landscape genomics and citizen science data. I'm also a director for the [rock pool project](https://www.therockpoolproject.co.uk/). I'm hoping to follow this into a career in academia but keeping an open mind along the way.

Previously I was at Exeter (Penryn) for both my BSc in Evolutionary Biology and my two-year Master by Research. At Exeter I was investigating the range expansion of the [St Piran’s hermit crab](https://www.therockpoolproject.co.uk/st-pirans-hermit-crab/), Clibanarius erythropus, to the southwest UK using, [population size and morphology surveys](https://mbr.biomedcentral.com/articles/10.1186/s41200-020-00186-1), population genetics and larval dispersal models. I grew up just outside of Leeds on the boundary of the Yorkshire dales.

You've found my github website where I aim to share interesting and fun things I've made.

Outside of lockdown, I head out climbing, orienteering, sea swimming, and cycling.

Feel free to reach out by [email anytime](http://www.conservationecology.org/christophe-patterson.html)! I'm also on Twitter where you can find me usually tweeting around life as a PhD student ([Christophe_Patt ](https://twitter.com/Christophe_Patt)) and the rock pool project, with some occasional grumblings around cycling infrastructure.